The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-13 Manuscript/NBABubbleAnalysis.Rmd
should use fisher.test for winning ratio

# Data {#sec:data}
Data were collected from the official NBA website. The main variables of interest
are whether or not the home team won, scoring totals for home and away teams, and
shooting percentages for home and away teams on two-pointers, three-pointers, and
free throws. These variables were very popular and frequently used in the related
literature discussed earlier. The data was collected on a game by game basis, this gave us two observations
for each variable per game played, one observation for each team(home and away).
There were 83 games played in the 2020 playoffs. Giving us 83 observations 
for each variable in 2020 for both the home and away teams(166 observations total). 
Likewise, there were 243 games played over 2017-2019. Giving us 243 observations of each variable 
for both home and away teams over 2017-2020(486 observations total).
While many other measures could be used for measuring
the outcome of the game and team performance, scoring seemed to be the most
important. The winner of a game is determined by who scores more points. There can only be
one winner and one loser making the outcome a binary variable. Each game has a winner 
denoted by a 1 in the W.L column of our data and a loser denoted by 0. Every game must result in 
exactly one team getting a 1 and exactly one team getting a 0. Winning percentage for home
(or away) teams can be conducted by summing the 1's for those teams together then dividing 
by the number of games played.

@@

>>>>

# Data {#sec:data}
Data were collected from the official NBA website. The main variables of interest
are whether or not the home team won, scoring totals for home and away teams, and
shooting percentages for home and away teams on two-pointers, three-pointers, and
free throws. These variables were very popular and frequently used in the related
literature discussed earlier. The data was collected on a game by game basis, this gave us two observations
for each variable per game played, one observation for each team(home and away).
There were 83 games played in the 2020 playoffs, giving 83 observations 
for each variable in 2020 for both the home and away teams (166 observations total). 
Likewise, there were 243 games played over 2017-2019,  giving 243 observations of each variable 
for both home and away teams over 2017-2020 (486 observations total).
While many other measures could be used for measuring
the outcome of the game and team performance, scoring seemed to be the most
important. The winner of a game is determined by who scores more points. There can only be
one winner and one loser making the outcome a binary variable, with
one indicating a win and zero indicating a loss.

@@

\emph{separate winning percentage from the other comparisons. Use
fisher.test for it}
